Batson Challenges Using Historical Data

### 2021-08-02 analysis/paper_draft.Rmd
revise section on historical data missingness

Prior work on statistical methods for _Batson_ challenges, however, have largely focused on strikes used in a single case taken alone. For example, @Barrett2007 modeled bias detection for _Batson_ challenges, given a "struck-jury" procedure in which the parties took turns striking prospective jurors. @Gastwirth2016 applied Fisher's exact test to detect bias in the pattern of strikes in each of ten published cases. For each of three cases, @Kadane2018 compared various frequentist approaches (including Fisher's exact test) with a Bayesian approach.

When considering strikes in multiple trials in the same State or judicial district, @Gastwirth2013 criticized the use of a paired t-test to compare the differences in strike rates of Black and non-Black venire members in the aggregate. Rather, both they and @Gastwirth2014 argued for applying the Cochran–Mantel–Haenszel test by taking the difference of the sum of the observed numbers of Black venire members challenged in each trial and the corresponding sum of the expected numbers of Blacks challenged, and then comparing it to the standard deviation of the difference.

Moreover, drawing inferences from peremptory challenges in past cases is hard, because jury-selection records are often not readily available and largely on paper, not electronic or machine-readable formats [@Grosso2017; @Wright2018], and otherwise require painstaking efforts to collect [e.g., @Craft2018].

This may matter for how much weight to assign such historical data if data on the use of strikes in past trials is missing not at random. For example, for any given attorney, there may be only incomplete information on that attorney's use of strikes in previous trials in a particular State or court. Possible reasons include limited access the relevant records (e.g., jury-selection records kept by a jury administrator, not in a case file) and the expense of obtaining copies of them.  Moreover, because some standard jury-selection forms do not require recording relevant juror information, such as juror race or gender, lawyers and researchers must turn to other data sources (e.g., voter registration rolls) with that information. Finally, regardless of what is supposed to be recorded, judges and court staff vary in how often they actually fill in standard forms with the required information.

>>>>

Prior work on statistical methods for _Batson_ challenges, however, has largely focused on strikes in a single case [e.g. @Barrett2007; @Gastwirth2016; @Kadane2018; @Kadane2018a]. When considering strike data in multiple trials from the same State or judicial district, @Gastwirth2013 criticized the use of a paired t-test to compare the differences in strike rates of Black and non-Black venire members in the aggregate. Rather, both they and @Gastwirth2014 argued for applying the Cochran–Mantel–Haenszel test by taking the difference of the sum of the observed numbers of Black venire members challenged in each trial and the corresponding sum of the expected numbers of Blacks challenged, and then comparing it to the standard deviation of the difference.

Part of the issue is that strike data from past cases is hard to collect. Jury-selection records are often not readily available and largely on paper, not electronic or machine-readable formats [@Grosso2017; @Wright2018], and otherwise require painstaking efforts to collect [e.g., @Craft2018].  As a result, even where there, for any given attorney, available strike data on past trials, that data may be missing strikes from trials not at random. Possible reasons include limited access the relevant records (e.g., jury-selection records kept by a jury administrator, not in a case file) and the expense of obtaining copies.  Some jurisdictions do not require recording relevant or detailed enough information about jurors who were or could have been struck, such as their race or gender. As a result, lawyers and researchers must expend time and effort to access other data sources (e.g., voter registration rolls) with that information. Finally, regardless of record-keeping policy, judges and court staff vary in how often they fully complete or maintain the required information.
